### 2020-10-08 input/background.tex
wip

\TODO{Multiple destinations shortest path \REF}.

@@

\TODO{Removing partition is more difficult.}

>>>>

\begin{definition}[Optimal partitioning]
  The optimal partitioning $\mathcal{P}$ is a set of logical
  partitions such that each process belongs to a logical partition
  comprising its closest source process. $\forall p \in P_{s_1},
  \nexists P_{s_2}$ such that \TODO{$distance(p, s_2) < distance(p,
    s_1)$}.
\end{definition}

When $distance$ involves monotonically increasing scalars such as
latency or number of hops between sources and processes, the optimal
partitioning consists in processing the multiple destinations shortest
path~\REF at each process. \TODO{Easy to solve when all processes
  receives all messages.}

@@

\begin{figure*}
  \begin{center}
    \subfloat[Part A]{\label{fig:addA}Meow}{input/figaddA.tex}
    \hspace{5pt}
    \subfloat[Part A]{\label{fig:addA}Meow}{input/figaddA.tex}
  \end{center}
\end{figure*}

Transitive relationships ensure that each process gets its closest
source while accumulators ensure that messages propagation
terminates. The system converges towards the optimal partitioning
despite processes not broadcasting all messages. Removals of
partitions are more challenging. \TODO{Figure.} One could solve this
issue by removing partitions that were not advertised for a defined
time~\REF. However, relying on physical timeout could lead to either
premature removals of partitions when they are still operating; or
slow convergence where processes believe they belong to a partition
that was removed.

\TODO{Problem statement.}

\TODO{Next Section presents our approach that solves this problem
  statement by relying only on logical control information.}
